Optimal Task Phasing for End-To-End Latency in Harmonic and Semi-Harmonic Automotive Systems

### 2024-09-26 paper.tex
ce chains

\section{Cause-Effect Chains and End-to-End latencies}

	A specific path in the data dependency graph is called a cause-effect chain $E$.
	We denote a cause-effect chain by $E=(\tau_1 \to \dots \to \tau_n)$ for some $n\in \Nbb$.
%
	To ensure proper timely behavior of the system, each cause-effect chain is equipped with a timing requirement, i.e., an upper bound $B \in \Rbb>0$ on the \emph{end-to-end latency} along the cause-effect chain $E$.

>>>>

\section{Cause-Effect Chains and End-to-End latencies}
\label{sec:e2e}

	To achieve complex functionalities, usually several tasks have to cooperate. 
	A sequence of cooperating tasks is called a cause-effect chain $E=(\tau_1 \to \dots \to \tau_n)$ with $n\in \Nbb_{\geq 1}$.
	Specifically, data that is written by $\tau_i$ is read by $\tau_{i+1}$, for $i=1, \dots, n-1$.
	The underlying functionality is achieved when data has been propagated through all $n$ tasks. 
	\mario{I think we need a simple application-oriented example here}
